Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions

### 2022-12-15 paper/new/article.tex
Work on article

\begin{abstract}
	This paper discusses briefly four popular algorithms to solve optimization/minimization problems, beloginging to Quasi-Newton class: \textit{Davidon–Fletcher–Powell} (DFP), \textit{Broyden–Fletcher–Goldfarb–Shanno} (BFGS), \textit{limited memory BFGS} and \textit{Levenberg-Marquardt Algorithm} (LMA). These algorithms are implemented in \textit{Python language}, version 3.10 and uses \textit{SymPy}, \textit{SciPy} and \textit{NumPy} libraries. One of them, \textit{BFGS}, is implemented natively on the  \textit{SciPy} library and the rest are implemented by hand to provide useful insights about the inner operation of the algorithms. The results are, however, very surprising with a few exceptions: when the initial solution is placed in a region near the global minimum, almost all algorithms converges very quickly and the convergence becomes unpredictable when the initial solution is placed randomly in the search space.
\end{abstract}

>>>>

\begin{abstract}
	This paper discusses briefly four popular algorithms to solve optimization/minimization problems, beloginging to Quasi-Newton class: \textit{Davidon–Fletcher–Powel

		 is placed in a region near the global minimum, almost all algorithms converges very quickly and the convergence becomes unpredictable when the initial solution is placed randomly in the search space.
\end{abstract}
